Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-07-21 paper/main.tex
revision of methods

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
audio-description (i.e. the audio-only variant of the movie) that was broadcast
as an additional audio track for visually impaired listeners on Swiss public
television \citep{ForrestGumpGermanAD}.
% AO vs. AV: differences
The plot of the movie is already carried by an off-screen voice-over of the main
character Forrest Gump. In the largely identical audio-description, an
additional male narrator describes essential aspects of the visual scenery when
there is no off-screen voice, dialog, or other relevant auditory content.

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$2h \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first movie segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}.

% VIS study picture categories
All stimuli for the VIS study were used in a previous study
\citep{haxby2011common}. There were 24 unique greyscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
categories: human faces, human bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment
independent from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted location \citep{haeusler2016cutanno}.
% AO anno
For the analysis of the AO data, we extended another publicly available
annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns embedded in sentences spoken by
the narrator to describe the movie's missing visual content. Some categories
were created in such a way to reflect the six stimulus categories used in the
visual localizer experiment. Some additional categories were created to
semantically cluster nouns into categories ``that were obvious to make
sense''.\todo{yeah, well, sounds shit but that's basically it}.
% categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
% Zeit.
More specifically, nouns were categorized by the clue they provide about the
cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
its inherent persons (female, female name; male, male name, person), a person's
appearance (face, head; body, bodypart), and a scene's inherent objects (object,
furniture).
% reference to table
A complete overview of all categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules (see
Table. Minor corrections due to incorrectly applied rules were by the author
(see Table \ref{tab:descr-nouns-counts} for the counts in the whole stimulus and
the eight stimulus segments used during fMRI scanning).

\todo[inline]{so ist die Tabelle zu breit; schrift kleiner oder Text kürzen?
Könnte durchaus auch detaillierteren Text schreiben}

% rules Tabelle für descriptiven nouns
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    cateogries, annotation rules and examples (given in English). The categorie
    \texttt{++} also contains adverbial adjectives and adverbs}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & moveable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing a new setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\subsection{Procedure}
% questionnaire
In all three studies, participants filled out a questionnaire on their basic
demographic information and familiarity with the movie).
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

@@

% paradigm implementation
In all three studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.

@@

% preprocessing intro
All further analysis steps of the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software
Library}; \citep{smith2004fsl}) on a computer cluster running the
\href{https://www.debian.org}{Debian} GNU/Linux operating system. Software
packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

% actual preprocessing
Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as part of FSL.
% temporal filtering
High-pass temporal filtering was applied to every segment using a
Gaussian-weighted least-squares straight line with a cutoff period of
\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
% brain extraction
The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
% spatial smoothing
Data were spatially smoothed applying a Gaussian kernel with full width at half
maximum (FWHM) of \unit[4.0]{mm}.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.
% pre-whithening
Correction for local autocorrelation in the time series (prewhitening) was
applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
to improve estimation efficiency.

@@

For both naturalistic stimuli, we conducted a standard two-level general linear
model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps)
across the 8 segments for every subject. A subsequent, third-level analysis averaged contrast estimates over subjects.

@@

% procedure
First, both annotations were split into eight parts corresponding to the eight
stimulus segments.
% AO events
To create regressors for the AV analysis, we used all of the original 19
categories of descriptive nouns except \texttt{++}.
% pooling
Some categories that were similar but offered only a small
amount of counts were pooled resulting in eleven new categories (see Table
\ref{tab:ao-events}). Events that fell into one of the two setting-related
category but also into another category were treated as belonging to the
setting-related category (\texttt{se\_new} or \texttt{se\_old}).
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that segment.  \todo{wenn ich "null regressor" nehme, darf ich den ganzen
Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich,
Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control.
% nuissance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

@@

For a description of the five control conditions for movie cuts see Table
\ref{tab:av-events}.}

@@

% AV events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts into five categories (see Table
\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of locale
within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
(\texttt{vpe\_new}), and 5) a cut to familiar perspective (\texttt{vpe\_old}).
% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
\texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.

\begin{table*}[t]
    \caption{Overview of events to build the 14 regressors for the analysis of the audio-only (AV) stimulus.
\texttt{fg\_av\_ger\_lr} (left-right difference in [+++???+++] of
consecutive movie frames).
\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames).
\texttt{fg\_av\_ger\_ud} (up-down difference in [+++???+++] of consecutive movie frames).
\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
For description of the two events categories of the audio-description's
narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast
of negative control see Table \ref{tab:ao-events}}
\label{tab:av-events}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\toprule
\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
% vpe_old has no events in 3. So the indices are shifted
vpe\_old & change of the camera position within a recurring locale & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII \tabularnewline
se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
fg\_av\_ger\_lr & XYZ & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
fg\_av\_ger\_ml & +++???+++ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
fg\_av\_ger\_pd & +++???+++ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
fg\_av\_ger\_ud & +++???+++ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
\end{tabular}
\end{table*}

% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the regressors of the AO and AV stimulus
and across the time course of all stimulus segments can be seen in Figure
\ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

\todo[inline]{contrasts are ordered by ``how well they make sense'' according to
theory, ``quality of auditory cue'', and amount of events/data. Hence, they were
assumed to result in more and more shitty results; at the moment all 8 contrasts
are used in the result (figure)}

% intro
For the AO stimulus, we created eight $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind
descriptive nouns.
% furniture: blurred border between groom and object
The categroy ``furniture'' (\texttt{furn} was not included in one of the
contrast because it can be considered as an object or geometry-defining
structure of a room.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts} we created for negative
control purposes to test if increased activation in the PPA was correlated with
moment of cuts and therefore correlated with a possible change in the
soundscape.

>>>>

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
audio-description that was broadcast as an additional audio track for visually
impaired listeners on Swiss public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by an voice-over of the main character
Forrest Gump.
% AO: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first movie segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}).

% VIS study picture categories
All stimuli for the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
categories: human faces, human bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

% stimuli were not designed for research purposes
Both natural stimuli were originally designed to entertain an audience and to
capture attention free from any perceptual or behavioral task.
% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
In/for the movie, We annotated different kinds of cinematographic cuts
\citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
% rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer in the depicted environment independent from the exact visual content in
the movie frame following the cut.

% AO anno
For the analysis of the AO data, we extended another publicly available
annotation of speech \citep{haeusler2020speechanno} by annotating words embedded
in sentences spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that describe the movie's
missing visual content.
% why and how of categories 1
Some categories were created in such a way to reflect the six stimulus
categories used in the visual localizer experiment.
% why and how of categories 2
Some additional categories were created to semantically cluster nouns into
categories ``that were obvious to make sense''.\todo{yeah, well, sounds shit but
that's basically it}
% categories in detail
Nouns were categorized by the verbal clue they provide about the
cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
its inherent persons (female, female name; male, male name, person), a person's
appearance (face, head; body, bodypart), and a scene's inherent objects (object,
furniture).
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus
segments used during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

\todo[inline]{currently table is to wide; smaller font? less text? rotate the table?}

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    categories, annotation rules, and examples (given in English). The category
    \texttt{++} also contains adverbial adjectives and adverbs.}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing a new setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\subsection{Procedure}
% questionnaire
In all three studies, participants filled out a questionnaire on their basic
demographic information and familiarity with the movie.
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

@@

% paradigm implementation
In all three studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the NeuroDebian operating system \citep{halchenko2012open}.

@@

% preprocessing intro
All further analysis steps of the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

% actual preprocessing
Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as part of FSL.
% temporal filtering
High-pass temporal filtering was applied to every stimulus segment using a
Gaussian-weighted least-squares straight line with a cutoff period of
\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
% brain extraction
The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
% spatial smoothing
Data were spatially smoothed applying a Gaussian kernel with full width at half
maximum (FWHM) of \unit[4.0]{mm}.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.
% pre-whithening
Correction for local autocorrelation in the time series (prewhitening) was
applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
to improve estimation efficiency.

@@

Similar to the reviewed studies employing simplified stimuli, we conducted a
standard two-level general linear model (GLM) analysis to create
subject-specific results ($Z$-maps) across the 8 segments for every subject. A
subsequent, third-level analysis averaged contrast estimates over subjects.

@@

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AV analysis, we used all of the original 19
categories of descriptive nouns except \texttt{++}.
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories (see Table \ref{tab:ao-events}) that
served as experimental conditions.
% setting beats other category
Events that fell into one of the two setting-related category but also into
another category were treated as belonging to the setting-related category
(\texttt{se\_new} or \texttt{se\_old}).
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf ich den ganzen
Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich,
Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuissance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

@@

For a description of the five control conditions for movie cuts see Table \ref{tab:av-events}.}

@@

% AV events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts into five categories (see Table
\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of room/locale
within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
(\texttt{vpe\_new}), and 5) a cut to a familiar perspective (\texttt{vpe\_old}).
% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.

\begin{table*}[t]
    \caption{Overview of events to build the 14 regressors for the analysis of the audio-only (AV) stimulus.
\texttt{fg\_av\_ger\_lr} (left-right difference in [+++???+++] of
consecutive movie frames).
\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames).
\texttt{fg\_av\_ger\_ud} (up-down difference in [+++???+++] of consecutive movie frames).
\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
For description of the two event categories of the audio-description's
narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast
of negative control see Table \ref{tab:ao-events}.}
\label{tab:av-events}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\toprule
\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
% vpe_old has no events in 3. So the indices are shifted
vpe\_old & change of the camera position within a recurring locale & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII \tabularnewline
se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
fg\_av\_ger\_lr & XYZ & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
fg\_av\_ger\_ml & +++???+++ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
fg\_av\_ger\_pd & +++???+++ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
fg\_av\_ger\_ud & +++???+++ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
\end{tabular}
\end{table*}

% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the regressors of the AO and AV stimulus
across the time course of all segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

\todo[inline]{contrasts are ordered by ``how well they make sense'' according to
theory, and amount of events/data. Hence, they were assumed to result in more
and more shitty results; at the moment all 8 contrasts are used in the result
(figure) despite the low ranked COPEs yielded 0 result as kinda expected}

% intro
For the AO stimulus, we created eight $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of
descriptive nouns.
% furniture: blurred border between groom and object
The category ``furniture'' (\texttt{furn}) was not included in one of the
contrasts as regressor if interest because it can be considered as an object or
geometry-defining structure of a room/locale.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created for negative
control purposes to test if increased activation in the PPA was correlated with
moment of cuts and therefore correlated with a possible change in the
soundscape.
